\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}


\begin{document}
\section*{1985{-}11{-}1}
But there's a lot of wonderful, legal stuff you can do with computers now, you don't have to break into somebody else's just to learn. There's a training minicomputer, and a 10{-}meg local mini just for the Center, and a lab{-}full of student PC clones and half{-}a{-}dozen Macs or so. Simple things, sometimes, but vital rules of thumb for street cops, who nowadays often stumble across a busy computer in the midst of a drug investigation or a white{-}collar bust. In 1991, the Well's list of conferences looked like this:               CONFERENCES ON THE WELL          WELL "Screenzine" Digest {-} (g zine)       Best of the WELL {-} vintage material {-} (g best)   Index listing of new topics in all conferences {-} (g newtops)             Business {-} Education            {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}   Apple Library Users Group (g alug)  Agriculture (g agri) Brainstorming     (g brain)   Classifieds (g cla) Computer Journalism  (g cj)    Consultants (g consult) Consumers       (g cons)   Design    (g design) Desktop Publishing   (g desk)   Disability  (g disability) Education       (g ed)    Energy    (g energy91) Entrepreneurs     (g entre)   Homeowners  (g home) Indexing        (g indexing) Investments (g invest) Kids91         (g kids)   Legal    (g legal) One Person Business  (g one) Periodical/newsletter (g per) Telecomm Law      (g tcl)    The Future  (g fut) Translators      (g trans)   Travel    (g tra) Work          (g work)           Electronic Frontier Foundation  (g eff)         Computers, Freedom \& Privacy   (g cfp)  Computer Professionals for Social Responsibility (g cpsr)             Social {-} Political {-} Humanities         {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}   Aging         (g gray)   AIDS     (g aids) Amnesty International (g amnesty)  Archives   (g arc) Berkeley        (g berk)   Buddhist   (g wonderland) Christian       (g cross)   Couples   (g couples) Current Events     (g curr)   Dreams    (g dream) Drugs         (g dru)    East Coast  (g east) Emotional Health****  (g private)  Erotica   (g eros) Environment      (g env)    Firearms   (g firearms) First Amendment    (g first)   Fringes of Reason (g fringes) Gay          (g gay)    Gay (Private)\# (g gaypriv) Geography       (g geo)    German    (g german) Gulf War        (g gulf)   Hawaii    (g aloha) Health         (g heal)   History   (g hist) Holistic        (g holi)   Interview  (g inter) Italian        (g ital)   Jewish    (g jew) Liberty        (g liberty)  Mind     (g mind) Miscellaneous     (g misc)   Men on the WELL** (g mow) Network Integration  (g origin)  Nonprofits  (g non) North Bay       (g north)   Northwest  (g nw) Pacific Rim      (g pacrim)  Parenting  (g par) Peace         (g pea)    Peninsula  (g pen) Poetry         (g poetry)  Philosophy  (g phi) Politics        (g pol)    Psychology  (g psy) Psychotherapy     (g therapy)  Recovery\#\#  (g recovery) San Francisco     (g sanfran)  Scams    (g scam) Sexuality       (g sex)    Singles   (g singles) Southern        (g south)   Spanish   (g spanish) Spirituality      (g spirit)  Tibet    (g tibet) Transportation     (g transport) True Confessions (g tru) Unclear        (g unclear)  WELL Writer's Workshop*** (g www) Whole Earth      (g we)    Women on the WELL* (g wow) Words         (g words)   Writers   (g wri)   **** Private Conference {-} mail wooly for entry ***Private conference {-} mail sonia for entry ** Private conference {-} mail flash for entry * Private conference {-} mail reva for entry \# Private Conference {-} mail hudu for entry \#\# Private Conference {-} mail dhawk for entry             Arts {-} Recreation {-} Entertainment         {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}   ArtCom Electronic Net (g acen) Audio{-}Videophilia   (g aud) Bicycles        (g bike)   Bay Area Tonight** (g bat) Boating        (g wet)    Books    (g books) 's          (g cd)    Comics    (g comics) Cooking        (g cook)   Flying    (g flying) Fun          (g fun)    Games    (g games) Gardening       (g gard)   Kids     (g kids) Nightowls*       (g owl)    Jokes    (g jokes) MIDI          (g midi)   Movies    (g movies) Motorcycling      (g ride)   Motoring   (g car) Music         (g mus)    On Stage   (g onstage) Pets          (g pets)   Radio    (g rad) Restaurant       (g rest)   Science Fiction (g sf) Sports         (g spo)    Star Trek  (g trek) Television       (g tv)    Theater   (g theater) Weird         (g weird)   Zines/Factsheet Five (g f5)   * Open from midnight to 6am ** Updated daily                   Grateful Dead                {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}   Grateful Dead     (g gd)    Deadplan*  (g dp) Deadlit        (g deadlit)  Feedback   (g feedback) GD Hour        (g gdh)    Tapes    (g tapes) Tickets        (g tix)    Tours    (g tours)   * Private conference {-} mail tnf for entry                  Computers               {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}   AI/Forth/Realtime   (g realtime) Amiga    (g amiga) Apple         (g app)    Computer Books (g cbook) Art \& Graphics     (g gra)    Hacking   (g hack) HyperCard       (g hype)   IBM PC    (g ibm) LANs          (g lan)    Laptop    (g lap) Macintosh       (g mac)    Mactech   (g mactech) Microtimes       (g microx)  Muchomedia  (g mucho) NeXt          (g next)   OS/2     (g os2) Printers        (g print)   Programmer's Net (g net) Siggraph        (g siggraph) Software Design (g sdc) Software/Programming  (g software) Software Support    (g ssc) Unix          (g unix)   Windows   (g windows) Word Processing    (g word)              Technical {-} Communications          {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}   Bioinfo        (g bioinfo)  Info     (g boing) Media         (g media)   NAPLPS    (g naplps) Netweaver       (g netweaver) Networld   (g networld) Packet Radio      (g packet)  Photography (g pho) Radio         (g rad)    Science   (g science) Technical Writers   (g tec)    Telecommunications (g tele) Usenet         (g usenet)  Video    (g vid) Virtual Reality    (g vr)                 The WELL Itself              {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}   Deeper         (g deeper)  Entry    (g ent) General        (g gentech)  Help     (g help) Hosts         (g hosts)   Policy    (g policy) System News      (g news)   Test     (g test)     The list itself is dazzling, bringing to the untutored eye a dizzying impression of a bizarre milieu of mountain{-} climbing Hawaiian holistic photographers trading true{-}life confessions with bisexual word{-}processing Tibetans. ** Page 9  With these facilities grew the demand for remote access to computers, and modern data communications began. With the ease of long habit, you are scanning your board for lit{-}up bulbs. We program, for hours on end, filled with a wild pioneering spirit, as if our task were to draw a line on the edge of the universe. Bring the switch to its knees, with say the UNIX "makedir" bug, and 911 goes down too as a matter of course. Large networks of interstate computers, linked over state lines, are also considered to be of "Federal interest." (This notion of "Federal interest" is legally rather foggy and has never been clearly defined in the courts. The scale may be very interesting, but it is clearly secondary, just as secondary as the various areas and fields from which the members of Minus Delta T come.\textbackslash{} Tonight, I went out for 1 hours. It was 42 degrees, was rained 0.0 inches. At Englishtown 2 I found DMS100 manuals. At Lakewood 2 I found DMS100 manuals. At Manasquan I found 5ESS manuals. At Browntown I found 5ESS manuals. At Manasquan I found 5ESS manuals. At Toms River 2 I found 5ESS manuals. At Middletown I found DMS100 manuals. But, I had to stop because I was out of fuel.


\end{document}